LabMate: a prospectus for types for MATLAB

### 2024-04-12 writing/IMEKOWC2024/LabMate/paper.tex
[ writing ] bash the bibstyle
[ writing ] honesty at first

@@

LabMate is under constant development; the latest version can be found at \url{https://github.com/msp-strath/LabMate/tree/devel}.

@@

\bibliographystyle{ws-procs9x6}
\bibliography{labmate}
%\printbibliography
\end{document}

>>>>

LabMate is under constant development; the latest version can be found at \url{https://github.com/msp-strath/LabMate/tree/devel}.
%
At time of writing, the necessary core type system is in place: we are busily extending the variety of MATLAB expressions it can make sense of, and the constraints it can solve.
%
We are close to covering the examples in this paper, but not quite there yet.
%
We aim to eliminate the speculative future tense from our examples before camera-ready copy is required.
%
This paper effectively documents how far we have come, and the roadmap to our next milestone.

@@

@@

%\bibliographystyle{ws-procs9x6}
\bibliographystyle{plain}
\bibliography{labmate}
%\printbibliography
\end{document}
